TODO: A Survey of StarCraft AI Techniques

### 2012-02-26 survey.tex
micro: state of the art with potential fields

>>>>

Potential fields \cite{Hagelback08,Hagelback09} are a powerful way to specify complex (with the combination of several fields, requiring a parameter-tuning method) behavior policies and are used in modern commercial games and RTS AI are using derivative of it (Supreme Commander flowfield). Self-organizing-maps (SOM) learned with evolutionary algorithms provide some way to learn (realistic) parameters for RTS units behavior \cite{teamCompositionRTS}. Bayesian programming has been applied to inverse fusion of the sensory inputs of the units \cite{SynnaeveMicroCig11}, which subsumes potential fields, allowing for integration of tactical goals directly in micro-management. There are also some cognitive approaches to RTS AI \cite{SORTS}, in which there is a human-like attention model for micro-management.
